Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-11 paper/paper.tex

>>>>

\begin{figure}[H]
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}-}
\end{figure}
